Annotation-Based Empirical Performance Tuning Using Orio

### 2009-02-12 doc/papers/ipdps09/results.tex
git-svn-id: https://svn.mcs.anl.gov/repos/performance/orio@433 e7ad4b5f-b827-0410-872f-f7f4bc3d1efb

@@

\begin{figure}%[tb]
\begin{tabular}{c}
\begin{minipage}[b]{.47\textwidth}
\centering
\includegraphics[width=1.0\textwidth]{figures/spmv.eps}  
\end{minipage}
\\
{\footnotesize (a)}
\\
\begin{minipage}[b]{.3\textwidth}
\scriptsize
\begin{verbatim}

@@

In the following sections, we refer to the icc-optimized base code as
``ICC,'' the Pluto-generated code with L1 tiling and
unroll/jamming as ``Pluto (L1 tiling),'' and the Pluto-generated code with L1
and L2 tilings and unroll/jamming as ``Pluto (L1+L2 tiling).'' The code
tuned by Orio is referred to as ``Pluto+Orio.''

@@

%
\begin{figure}
\begin{center}
\begin{minipage}{3in} 
\scriptsize
\begin{verbatim} 
for(t=0; t<tmax; t++) { 
  for (j=0; j<ny; j++) ey[0][j] = t; 
  for (i=1; i<nx; i++) 
    for (j=0; j<ny; j++) 
      ey[i][j] -= 0.5*(hz[i][j] - hz[i-1][j]); 
  for (i=0; i<nx; i++) 
    for (j=1; j<ny; j++) 
      ex[i][j] -= 0.5*(hz[i][j] - hz[i][j-1]); 
  for (i=0; i<nx; i++) 
    for (j=0; j<ny; j++) 
      hz[i][j] -= 0.7*(ex[i][j+1] - ex[i][j]
                  + ey[i+1][j] - ey[i][j]); 
} 
\end{verbatim} 
\end{minipage} 
\end{center}
\caption{2-D FDTD code.} 
\label{fig:fdtd-2d-code} 
\end{figure}
%

@@

\subsubsection{3-D Gauss-Seidel Successive Overrelaxation Method}  
Figure~\ref{fig:seidel-code} shows the 3-D Gauss-Seidel computation, 
which is sometimes referred to as
\emph{successive displacement method}, indicating the dependence of the 
iterations on the ordering. If the ordering is changed, the components
of the new iterations will change as well.
%
%\begin{figure}[ht]
\begin{figure}%[ht]
\begin{center}
\begin{minipage}{3in} 
\scriptsize
\begin{verbatim} 
for (t=0; t<=T-1; t++) 
  for (i=1; i<=N-2; i++) 
    for (j=1; j<=N-2; j++) 
      A[i][j] = (A[i-1][j-1] + A[i-1][j] 
          + A[i-1][j+1] + A[i][j-1] + A[i][j] 
          + A[i][j+1] + A[i+1][j-1] + A[i+1][j] 
          + A[i+1][j+1]) / 9.0; 
\end{verbatim} 
\end{minipage} 
\end{center}
\caption{3-D Gauss-Seidel code} 
\label{fig:seidel-code} 
\end{figure}
%

@@

LU factorization or decomposition is a numerical method for the
solution of linear systems of equations; a simple implementation is
shown in Figure~\ref{fig:lu-code}.
%
\begin{figure}%[ht]
\begin{center}
\begin{minipage}{2.8in} 
\scriptsize
\begin{verbatim} 
for (k=0; k<=N-1; k++) { 
  for (j=k+1; j<=N-1; j++) 
    A[k][j] /= A[k][k]; 
  for(i=k+1; i<=N-1; i++) 
    for (j=k+1; j<=N-1; j++) 
      A[i][j] -= A[i][k]*A[k][j]; 
} 
\end{verbatim} 
\end{minipage} 
\end{center}
\caption{LU decomposition code.} 
\label{fig:lu-code} 
\end{figure}
%

>>>>

\begin{figure}%[b]
\begin{tabular}{c}
\begin{minipage}[t]{.47\textwidth}
\centering
\vspace{0.2in}
\includegraphics[width=1.0\textwidth]{figures/spmv.eps}  
\end{minipage}
\\
{\footnotesize (a)}
\\
\begin{minipage}[t]{.3\textwidth}
\scriptsize
\begin{verbatim}

@@

@@

In the following sections, we refer to the icc-optimized base code as
xs``ICC,'' the Pluto-generated code with L1 tiling and
unroll/jamming as ``Pluto (L1 tiling),'' and the Pluto-generated code with L1
and L2 tilings and unroll/jamming as ``Pluto (L1+L2 tiling).'' The code
tuned by Orio is referred to as ``Pluto+Orio.''

@@

\begin{figure}
\begin{center}
\begin{minipage}{3in} 
\scriptsize
\begin{verbatim} 
for(t=0; t<tmax; t++) { 
  for (j=0; j<ny; j++) ey[0][j] = t; 
  for (i=1; i<nx; i++) 
    for (j=0; j<ny; j++) 
      ey[i][j] -= 0.5*(hz[i][j] - hz[i-1][j]); 
  for (i=0; i<nx; i++) 
    for (j=1; j<ny; j++) 
      ex[i][j] -= 0.5*(hz[i][j] - hz[i][j-1]); 
  for (i=0; i<nx; i++) 
    for (j=0; j<ny; j++) 
      hz[i][j] -= 0.7*(ex[i][j+1] - ex[i][j]
                  + ey[i+1][j] - ey[i][j]); 
} 
\end{verbatim} 
\end{minipage} 
\end{center}
\caption{2-D FDTD code.} 
\label{fig:fdtd-2d-code} 
\end{figure}

\begin{figure}%[ht]
\begin{center}
\begin{minipage}{3in} 
\scriptsize
\begin{verbatim} 
for (t=0; t<=T-1; t++) 
  for (i=1; i<=N-2; i++) 
    for (j=1; j<=N-2; j++) 
      A[i][j] = (A[i-1][j-1] + A[i-1][j] 
          + A[i-1][j+1] + A[i][j-1] + A[i][j] 
          + A[i][j+1] + A[i+1][j-1] + A[i+1][j] 
          + A[i+1][j+1]) / 9.0; 
\end{verbatim} 
\end{minipage} 
\end{center}
\caption{3-D Gauss-Seidel code} 
\label{fig:seidel-code} 
\end{figure}

\begin{figure}%[ht]
\begin{center}
\begin{minipage}{2.8in} 
\scriptsize
\begin{verbatim} 
for (k=0; k<=N-1; k++) { 
  for (j=k+1; j<=N-1; j++) 
    A[k][j] /= A[k][k]; 
  for(i=k+1; i<=N-1; i++) 
    for (j=k+1; j<=N-1; j++) 
      A[i][j] -= A[i][k]*A[k][j]; 
} 
\end{verbatim} 
\end{minipage} 
\end{center}
\caption{LU decomposition code.} 
\label{fig:lu-code} 
\end{figure}

@@

\subsubsection{3-D Gauss-Seidel Successive Overrelaxation Method}  
Figure~\ref{fig:seidel-code} shows the 3-D Gauss-Seidel computation, 
which is sometimes referred to as
\emph{successive displacement method}, indicating the dependence of the 
iterations on the ordering. If the ordering is changed, the components
of the new iterations will change as well.

@@

LU factorization or decomposition is a numerical method for the
solution of linear systems of equations; a simple implementation is
shown in Figure~\ref{fig:lu-code}.
